Modeling vertical-axis cross-flow turbine wakes

### 2015-03-12 paper.tex
Add more basic things

\documentclass[aip,graphicx]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}

@@

\author{Peter Bachant}
\email[]{pxL3@unh.edu}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Center for Ocean Renewable Energy, University of New Hampshire, 
Durham, NH}

@@

\maketitle %\maketitle must follow title, authors, abstract and \pacs

@@

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% Put your acknowledgments here.
%\end{acknowledgments}

>>>>

\documentclass[aip,graphicx]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}
\usepackage[draft]{todonotes}

@@

\author{Peter Bachant}
\email[]{pxl3@unh.edu}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Center for Ocean Renewable Energy, University of New Hampshire, 
Durham, NH}

@@

\maketitle %\maketitle must follow title, authors, abstract and \pacs
\listoftodos

@@

\section{Results}

\subsection{Performance prediction}

Predictions for both the power and drag coefficients are shown in Figure~\ref{fig:perf_comp}

\begin{figure}
\caption{Power (a) and drag (b) coefficient predictions from experiments and
each numerical model.}
\label{fig:perf_comp}
\end{figure}

\todo[inline]{Add bar graph comparing various performance results for the RVAT.}

\begin{acknowledgments}
The authors acknowledge Vincent Neary and the Sandia National Laboratories Water
Power Program for use of their Red Mesa high performance computing cluster.
\end{acknowledgments}
